Does pre-crastination explain why some observers are sub-optimal in a visual search task?

### 2024-01-17 RegReport/paper_nomarkup.tex
added missing end bracket in abstract

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we asked whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we asked 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. Based on pilot data, we predicted an association of pre-crastination with inefficient search strategies. Personality inventories were also administered to identify stable characteristics associated with these strategies. In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

Stimuli were presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Stimulus generation, presentation and data collection were controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.

@@

We collected data from a grand total of 305 participants. 14 of these participants had to be removed due to missing eyetracking data. Out of the 291 remaining, 90 failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. 303 participants completed the precrastination task (one participant was excused from this part of the experiment because of a \textcolor{red}{broken} leg, and another for an unspecified reason). 304 participants completed the personality questionnaires (\textcolor{red}{20} participants had blank or otherwise unusable data).

@@

Each participant’s median reaction time and accuracy was computed for the split-half visual
search task, presented in Figure \ref{fig:exp2_summary}. The results are broadly in-line with those that we have seen in previous uses of this paradigm. More importantly, we see large variation in search strategy (\ref{fig:exp2_strat_summary}(a), replicating previous results. \textcolor{red}{The standard deviation of our efficiency score is 0.192.}

>>>>

% \maketitle
\begin{abstract}
How do we decide where to search for a target? Optimal search relies on first considering the relative informational value of different locations, and then executing eye movements to the best options. But many participants consistently move their eyes to locations that can be easily ascertained to neither contain the target, nor to provide new information about the target's location. Here we asked whether this sub-optimal search behaviour represents a specific example of a general tendency towards \textit{pre-crastination}: starting sub-goals of a task before they are needed, and in so doing, spending longer doing the task than is necessary. To test this hypothesis, we asked 200 participants to do two tasks: retrieve two heavy buckets (one close and one far), and search for a line segment. Pre-crastination is defined as consistently picking up the closer bucket first, versus the more efficient strategy of picking up the farther bucket first. Search efficiency is the proportion of fixations directed to more cluttered regions of the search array. Based on pilot data, we predicted an association of pre-crastination with inefficient search strategies. Personality inventories were also administered to identify stable characteristics associated with these strategies. In the final dataset, there was no clear association between search strategy and pre-crastination, nor did these correlate strongly with any of the personality measures collected.}
\end{abstract}

@@

Most of the data was collected at the University of Aberdeen. Stimuli were presented on a 17 inch CRT monitor with a resolution of $1024 \times 768$. Around a third of participants were tested at the university using a 21 inch LCD panel with a resolution of $1920 \times 1080$. The display distance was set so that the visual angle of the stimuli was approximately the same between the two sites. Stimulus generation, presentation and data collection were controlled by Matlab and psychophysics toolbox \cite{brainard1997,cornelissen2002} run on a mac pro computer. The position of the right eye was recorded using a desktop-mounted EyeLink 1000 eye tracker (SR Research, Canada) sampling eye position at 1000Hz.

@@

We collected data from a grand total of 305 participants. 14 of these participants had to be removed due to missing eyetracking data. Out of the 291 remaining, 90 failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. 303 participants completed the precrastination task (one participant was excused from this part of the experiment because of a broken leg, and another for an unspecified reason). 304 participants completed the personality questionnaires (20 participants had blank or otherwise unusable data).

@@

Each participant’s median reaction time and accuracy was computed for the split-half visual
search task, presented in Figure \ref{fig:exp2_summary}. The results are broadly in-line with those that we have seen in previous uses of this paradigm. More importantly, we see large variation in search strategy (\ref{fig:exp2_strat_summary}(a), replicating previous results.The standard deviation of our efficiency score is 0.192.
